### 2016-12-19 paper/chapters/abstract.tex
updated

\section{Abstract}
\label{sec:abstract}
Deep Learning has advanced at an incredible speed the last few years and has achieved human-level performance in some discrimination and classification tasks (object recognition, speech recognition).
These supervised methods have the huge drawback of requiring a vast amount of labelled data which is often expensive or unfeasible to obtain.
Learning hidden structure from unlabelled data known as unsupervised learning has had less of an impact recently.
However, it can be argued that this method is most similar to human learning, in particular inferring information from observations and building an appropriate model from it.
We will discuss and explore some models for performing this inference as well as generating new data from these representations.
Building reasonable representation of the world from unlabelled data is arguably one of the key aspects of machine intelligence.
%However one of the key aspects to machine intelligence is learning a rich (?) model about the world and draw conclusions from it.
%The above mentioned tasks require huge amount of labelled data to perform well, which is one of the restrictions of these supervised learning mechanisms.
%Unsupervised learning has the potential to make use of the vast unlabelled data surrounding the world.
%This data can be used to learn representations

>>>>

\section{Abstract}
\label{sec:abstract}
%One of the key aspects of human intelligence is the ability to construct accurate and generalized internal representations by observing high-dimensional data.
%We present several deep directed generative models aiming to learn rich and hierarchical latent structures, either implicitly or explicitly, as well as transforming them back into input space.

Deep directed generative models leverage the possibilities of deep learning to learn rich, hierarchical structures from datasets in a possibly unsupervised context.
These models can be used to understand high-dimensional, real-world data and transform them into compact representations. Similar to how humans learn to generalize from sensory input, we discuss several models which are able to learn compact, internal representational structures.
In this article we will focus on two recently proposed architectures, variational autoencoders and generative adversarial networks.

% maybe include:
% * unsupervised models are in high demand due to the massive increase in the amount of unlabelled data due to web, videos, internat in general, laboratory measurements, etc.

%Deep Learning has advanced at an incredible speed the last few years and has achieved human-level performance in some discrimination and classification tasks (object recognition, speech recognition).
%These supervised methods have the huge drawback of requiring a vast amount of labelled data which is often expensive or unfeasible to obtain.
%Learning hidden structure from unlabelled data known as unsupervised learning has had less of an impact recently.
%However, it can be argued that this method is most similar to human learning, in particular inferring information from observations and building an appropriate model from it.
%We will discuss and explore some models for performing this inference as well as generating new data from these representations.
%Building reasonable representation of the world from unlabelled data is arguably one of the key aspects of machine intelligence.
%However one of the key aspects to machine intelligence is learning a rich (?) model about the world and draw conclusions from it.
%The above mentioned tasks require huge amount of labelled data to perform well, which is one of the restrictions of these supervised learning mechanisms.
%Unsupervised learning has the potential to make use of the vast unlabelled data surrounding the world.
%This data can be used to learn representations

### 2016-12-19 paper/chapters/gan.tex
updated

@@

\subsubsection{Generator Network}
The generator $G$ in the GAN framework tries to fool the discriminator $D$ by producing samples which are indistinguishable from the training data.
This process can be formally written as minimizing the following cost function.
$$
\mathcal{L}_g = \min \log(1 - D(G(z)))
$$
Where $z$ is sampling from the noise prior $p(z)$.\\

Another common form of the generator loss is $\mathcal{L'}_g$.
$$
\mathcal{L'}_g = \max \log D(G(z))
$$
This formulation has the benefit of the same optimum fixed point, but has a better gradient flow early in training when $G$ produces samples which can be distinguished easily from real data by $D$.

@@

\paragraph{Theoretical Foundation}
Using a model with infinite training time and capacity in both generator and discriminator allows theoretical analysis of the GAN framework \cite{gan:2013}.
For any given generator $G$, the optimal discriminator $D$ is given by $D_G^*(x)$:
$$
D_G^*(x) = \frac{p_{data}(x)}{p_{data}(x) + p_{model}(x)}
$$

@@

@@

\subsection{Application}
\label{sub:gan_application}
GAN have been applied to many different areas which include generating images (GAN, DCGAN, LAPGAN), sequences (SeqGAN), videos (\cite{gan_video:2016}), 3D objects (\cite{gan_3d:2016}), text-to-image synthesis (\cite{gan_t2i:2016})

>>>>

\newpage

@@

\subsubsection{Generator Network}
The generator $G$ in the GAN framework tries to fool the discriminator $D$ by producing samples which are indistinguishable from the training data.
This process can be formally written as minimizing the following cost function.
%Where $z$ is sampling from the noise prior $p(z)$.\\

%Another common form of the generator loss is $\mathcal{L'}_g$.
%$$
$$
\mathcal{L}_g = \min \log(1 - D(G(z)))\\
\mathcal{L'}_g = \max \log D(G(z))
$$
This formulation has the benefit of the same optimum fixed point, but has a better gradient flow early in training when $G$ produces samples which can be distinguished easily from real data by $D$.

@@

\vspace{5cm}
\paragraph{Theoretical Foundation}
Using a model with infinite training time and capacity in both generator and discriminator allows theoretical analysis of the GAN framework \cite{gan:2014}.
For any given generator $G$, the optimal discriminator $D$ is given by $D_G^*(x)$:
$$
D_G^*(x) = \frac{p_{data}(x)}{p_{data}(x) + p_{model}(x)}
$$

@@

\vspace{10cm}

@@

\newpage

%\subsection{Application}
%\label{sub:gan_application}
%GAN have been applied to many different areas which include generating images (GAN, DCGAN, LAPGAN), sequences (SeqGAN), videos (\cite{gan_video:2016}), 3D objects (\cite{gan_3d:2016}), text-to-image synthesis (\cite{gan_t2i:2016})

### 2016-12-19 paper/chapters/introduction.tex
updated

\section{Introduction}
\label{sec:introduction}
Generative models are one of the most promising ways to perform unsupervised learning (citation needed).
More specifically, generative modelling assumes a hidden structure $z$ explaining the input data $x$.
This assumption is reasonable given the following examples:\\

\begin{itemize}
  \item \textbf{Images} often have multiple thousands of dimensions, but the underlying structure is often far simpler. For example are 28x28 images of handwritten digits 784-dimensional but assuming one-hot encoding the most important information - the digit - it can be explained using 10 dimensions. There are a few more dimensions, stroke width, cursive, position, size. But still far lower than 784. We will take a look at this example later on in \ref{sec:vae}.
  \item \textbf{Speech} or more precisely the recording of it is high-dimensional, while the information it carries (the spoken words) can be represented in a low-dimensional space.
  \item \textbf{...}
\end{itemize}

After a short overview of different approaches and methods and an introductory example with the sigmoid belief net (SBN), we will take a closer look at two promising frameworks, the variational autoencoder (VAE) and the generative adversarial network (GAN)

>>>>

\section{Introduction}
\label{sec:introduction}

"What I cannot create, I do not understand." -- Richard Feynman \\\\\\

Directed generative models are a wide class of models used for generating samples from an unknown distribution.
Lets denote $p_{data}(x)$ as the real-world data distribution which is unknown, however we have access to samples from it: $x \sim p_{data}(x)$.
In order to do so, we define an approximated distribution $p_{model}$ from which we are able to sample.
Under the assumption that $p_{model}$ approximates $p_{data}$ accurately, samples from the true data distribution should have high likelihood under the approximation as well.\\\\

Generative modelling has several important application areas, which will be highlighted on below.\\
Deep learning techniques have provided great success in applying gradient-based optimization methods to deep neural networks to achieve impressive results in discriminative models.
These models require however large amounts of labelled data, which is often expensive or infeasible to obtain.
Generative models can be used to learn \emph{representational} structures from rich, unlabelled data by having less parameters than the input data and are thus forced to capture only essential information.\\
\newpage

%Prior to discussion individual models, we need to declare a few assumptions and definitions.
%Additionally we assume that samples $x$ are also conditionally dependent on some hidden structure $z$: $x \sim p(x|z)$. 
%\begin{equation}
  %z \sim p(z)\\
  %x \sim p(x|z)
%\end{equation}

%\paragraph{Sampling}
%means for any given $z$ to draw a sample $x$ from our model.
%Most commonly, sampling is the easiest requirement to fulfil.

%\paragraph{Learning}
%of the model parameters through maximum likelihood estimation generally involves $p(x)$ or its gradient.\\
%To get $p(x)$, we first need to marginalize our the latent variables.
%\begin{equation}
  %p(x) = \sum_h p(x|z)p(z)
%\end{equation}
%Unfortunately, in the case of deep learning with many layers this is intractable, as we need to evaluate all model configurations.
%via maximum likelihood generally involves the gradients of $p(x)$
%\paragraph{Inference}
% motivation / what we want exactly and why
%Building intelligent systems requires having accurate and generalized information about the environment in order to perform actions or reason about the world.
%Inferring structured and meaning information from unlabelled data, a process called unsupervised learning, remains a challenging task.

%However, due to the massive increases in availability of data emerging from the web as well as the ongoing progress in computational power there has been significant progress using this data.

%Generative modelling aims to generate new data similar to previously seen input, in a way which is sound with the internal structure of the data.

%% on building reasonable representations
The assumption that data can be explained using an underlying, simpler structure than the raw input data is important to handle the high-dimensional nature of most data source.
In order to understand how these statistical models help us to discover the data structure, we will take a look at a few examples of high-dimensional real world data.
\begin{itemize}
  \item \textbf{Images} consisting of millions of pixels can be interpreted as data where each pixel represents an own dimension.
  However, these dimensions are high correlated and structured, for example nearby pixels have with high probability similar values.
  Looking at images of handwritten digits, the data can be reduced to a handful variables which may include the digit number, stroke width, position or size.
  Statistical models help us discover these relations and reduce them to representations in lower dimensional space.
  %\item commonly have thousands of dimensions, but the underlying structure is often far simpler. For example are 28x28 images of handwritten digits 784-dimensional but assuming one-hot encoding the most important information - the digit - it can be explained using 10 dimensions. There are a few more dimensions, stroke width, cursive, position, size. But still far lower than 784. We will take a look at this example later on in \ref{sec:vae}.
  \item \textbf{Audio data} is omni-present in the real world, however most data sources can be transformed from raw audio samples to spoken words or musical notes without losing too much information for reconstruction.
  \item \textbf{...}
\end{itemize}
% cope with
%To develop systems learning from real world data we use statistical models which are able to infer the underlying structure from
%Real world data is often high-dimensional and noise and transforming this data into an compact representation is therefore an important and also challenging task to perform.
%Generative models are ideal for this task since it has to understand the underlying structure to generate similar data.
%Building this structure is called \textbf{representation learning} and is key to many generative models and how they perform.\\

%With this assumption in mind we can take a look at some examples of input data.

The assumption that $p(x)$ is dependent on some underlying structure can now be expressed as having the conditional probability $p(x|z)$ where the latent variables $z$ are the causal factors. This stochastic dependency can be represented in a graphical model shown in figure \ref{fig:dgm}.\\

\begin{figure}[htb]
\centering
\includegraphics{media/directed_graphical_model}
  \caption{Directed graphical model}
  \label{fig:dgm}
  \medskip
  \small
  Arrows show stochastic dependency.
\end{figure}

%Inverting $p(x|z)$ yields $p(z|x)$ which is one of the main tasks of some generative models, for example the VAE \ref{sec:vae}.

%After a short overview of different approaches and methods and an introductory example with the sigmoid belief net (SBN), we will take a closer look at two recent promising frameworks, the variational autoencoder (VAE \ref{sec:vae}) and the generative adversarial network (GAN \ref{sec:gan}).

%Generative models are one of the most promising ways to perform unsupervised learning (citation needed).
%More specifically, generative modelling assumes a hidden structure $z$ explaining the input data $x$.
%This assumption is reasonable given the following examples:\\

### 2016-12-19 paper/chapters/overview.tex
updated

\paragraph{Sigmoid Belief Nets (SBN)}
\label{par:overview_sbn}
SBNs are one of the earliest generative models, using a simple architecture in which sampling from is easy, but learning and performing inference is not.

\paragraph{Differentiable Generator Networks}
Due to the success of gradient-based methods for learning deep networks, a large part of recent models are using a differentiable generator network which allows for error backpropagation.\\
Most prominent examples of models with differentiable generator nets are the variational autoencoder (VAE) \cite{vae:2014} and generative adversarial networks (GAN) \cite{gan:2014}.
These models include a generator networks representing a family of parametrized non-linear functions $g$ implemented usually implemented as neural networks.\\
Using $g$ as distribution transformation allows samples $z$ to be transformed into $x$ where the distribution over $x$ may be more complicated than $z$.
The parameters of $g$ can be inferred using training data and an appropiate loss function.\\
However, instead of maximizing the log-likelihood of $p(x)$ directly we choose $g$ to emit not samples of $x$ but parameters of a conditional distribution over $x$.

\paragraph{Auto-regressive networks}

>>>>

\subsection{Sigmoid Belief Nets}
\label{par:overview_sbn}
Sigmoid Belief Nets (SBN) are a specific type of bayesian networks consisting of an set of binary states with each state depending on activations of preceeding nodes.

Bayesian networks or belief networks are an probabilistic interpretation of an directed acyclic graphical model with a set of states $s$.
As usual in the bayesian framework, each state can be interpreted as a random variable with their conditional probabilities.
%SBNs are one of the earliest deep directed generative models, consisting of binary states $s$ most commonly divided into many layers.

%where in the most common form the architecture consists of several layers where each layer $h_i$ is connected from the previous layer $h_{i-1}$.
%Sampling is an easy task in this model, however inferring good structure for the first layer is a difficult task.
%Usually, in the context of probabilistic generative models we are mostly interested in three different aspects.
%First, sampling from the network. This means given 
%We are mostly interested in three different things involving

%\vspace{3cm}
%using a simple architecture in which sampling from is easy, but learning and performing inference is not.

\subsection{Differentiable Generator Networks}
Most of recent success in deep learning can be attributed to the backpropagation algorithm, including several useful extensions like dropout (citation), or piecewise-linear activation units providing a well-behaving gradient.
Most prominent examples of recent directed generative models leverage these powerful gradient-based optimization techniques by including a generator network.

Most prominent examples of models with differentiable generator nets are the variational autoencoder (VAE) \cite{vae:2014} and generative adversarial networks (GAN) \cite{gan:2014}, which we will discuss in detail later in \ref{sec:vae} and \ref{sec:gan} respectively.

%Due to the success of gradient-based methods for learning deep neural networks, a large part of recent models are using a differentiable generator network allowing error backpropagation.\\

%Both of these models contain a generator network coupled with another network which enables the models to be learned end-to-end.
Both models include generator networks representing a family of parametrized non-linear functions $g_\varphi$ parametrized by $\varphi$ where these parameters can be learned by gradient-based techniques.\\
As neural networks are basically powerful function approximators, they can also be understood as a distribution transformation.
Given samples $z$ from one distribution $p(z)$, applying $g$ is equivalent to sampling from the posterior distribution $p(x|z)$ which is generally more complicated than the prior $p(z)$.\\

%which transforms samples $z$ from a distribution $p(z)$ into $x$ values from a different, possible more complicated distribution $p(x|z)$.
The advantage of this approach is that powerful gradient-based optimization techniques can be used to learn the transformation $g$ without modifying the prior distribution $p(z)$.
The parameters of $g$ can be learned using training data and an appropiate loss function.\\
\newpage
%However, instead of maximizing the log-likelihood of $p(x)$ directly we choose $g$ to emit not samples of $x$ but parameters of a conditional distribution over $x$.

%\subsection{Auto-regressive networks}

### 2016-12-19 paper/chapters/sigmoid_belief_nets.tex
updated

\section{Sigmoid Belief Networks}
\label{sec:sbn}
Sigmoid Belief Networks (SBN) have been proposed in 1992 by R.M. Neal \cite{neal:1992} representing a a specific type of bayesian networks \cite{pearl:1985}.
They are one of the earliest neural networks used for generative modelling, predating all other presented models in this article.

These random variables are interpreted in a bayesian way where each one may be observed, hidden (or latent) or unknown representing different states of knowledge or belief \cite{definetti:1974}.
\begin{figure}[htb]
\centering
\input{media/sbn_architecture}
  \caption{SBN architecture}
  \label{fig:sbn_arch}
  \medskip
  \small
  Sigmoid Belief Network described as a acyclic directed graph where blue nodes indicate hidden variables while red nodes represent observed variables.
  Arrows show stochastic dependency. The dashed arrow indicates that it is possible in the original definition, even though most commonly the hidden variables are divided into layers.
\end{figure}

\subsection{Learning}
\begin{figure}[htb]
\centering
\includestandalone[mode=buildnew]{media/sbn_node}
  \caption{SBN node}
  \label{fig:sbn_node}
\end{figure}
In its most common form, SBNs are comprised by a number of layers where each node in a layer is a sigmoid function of its ancestors:
$$
p(s_i) = \sigma\bigg(\sum_{j<i}W_{i,j}s_j+b_i\bigg)
$$

>>>>

\section{Sigmoid Belief Networks}
\label{sec:sbn}
\begin{figure}[htb]
\centering
\input{media/sbn_architecture}
  \caption{Bayesian networks}
  \label{fig:sbn_arch}
  \medskip
  \small
  Bayesian networks or belief nets can be described as an acyclic directed graph where blue nodes indicate hidden variables while red nodes represent observed variables.
  Arrows show stochastic dependency. The dashed arrow indicates that it is possible in the original definition, even though most commonly the hidden variables are divided into layers.
\end{figure}

Sigmoid Belief Networks (SBN) have been proposed in 1992 by R.M. Neal \cite{neal:1992} representing a specific type of bayesian networks \cite{pearl:1985}.
\ref{fig:sbn_arch} shows a bayesian network as a graphical model with each state influenced by its ancestors.
In the case of SBNs however, the states are all binary and the activation function is the sigmoid function. They are one of the earliest neural networks used for generative modelling, predating all other presented models in this article.
%As described in the overview above, SBNs contain a number of binary states $s$, most commonly divided into many layers.
Each state $s_i$ is a random variables which may be observed, hidden or unknown representing different states of knowledge or belief. As such it can be interpreted with a probability distribution.
\begin{equation}
  \label{eq:sbn_node}
p(s_i) = \sigma\bigg(\sum_{j<i}W_{i,j}s_j+b_i\bigg)
\end{equation}
In equation \ref{eq:sbn_node}, $\sigma$ denotes the sigmoid function $\frac{1}{1 + e^{-x}}$ and $W_{i,j}$ the connection weights from state $s_j$ to $s_i$.

In probabilistic networks, we are mostly interested in the aspects: sampling, learning and inferring.
Even though sampling can be done efficiently, the other operations are intractable in almost all cases.
\paragraph{Sampling}
can be done using ancestral sampling through the hidden layers evaluating \ref{eq:sbn_node}

%These random variables are interpreted in a bayesian way where each one may be observed, hidden (or latent) or unknown representing different states of knowledge or belief \cite{definetti:1974}.

\newpage
\subsection{Learning}
\begin{figure}[htb]
\centering
\includestandalone[mode=buildnew]{media/sbn_node}
  \caption{SBN node}
  \label{fig:sbn_node}
\end{figure}

In its most common form, SBNs are comprised by a number of layers where each node in a layer is a sigmoid function of its ancestors:

### 2016-12-19 paper/chapters/vae.tex
moved the cropped version
updated

\section{Variational Autoencoders \cite{vae:2013}}
\label{sec:vae}
Variational Autoencoders (VAE) have been introduced in 2014 by Kingma and Welling which uses variational inference to perform efficient inference and learning in deep latent models.
Deep latent models are based on the assumption that input data can be explained using non-linear transformations coming from simple distributions. \cite{rezende:2014} (check!?).

@@

% move to architecture:
%In the original VAE paper, the unit gaussian distribution with diagonal variance was proposed for $p(z)$ and although there have been multiple proposals (citations, multi-modal etc) for different distributions we will stick with $\mathcal{N}(0,I)$ for the sake of simplicity.
% ---

@@

@@

We use VAEs when we have a complicated distribution $p_\theta(x,z)$ with unknown latent variables $z$.
The prior distribution $p(z)$ over the latent structure is a centered isotropic(?) multivariate Gaussian denoted by $\mathcal{N}(z;0, I)$.
The constructed architecture uses an probabilistic encoder $q_\theta(z|x)$ and a probabilistic decoder $p_\theta(x|z)$ in a form of neural networks, in the original paper MLP are used\cite{vae:2013} but there are various extensions (see \ref{sub:vae_extensions}, TODO).
Because the posterior is intractable ($p_\theta(x)$), we instead approximately maximize the lower variational bound $L(\theta,\phi;x)$.\\
\begin{equation}
  \mathcal{L}(\theta,\phi;x) = -D_{KL}(q_\theta(z|x)||p(z)) + \mathbb{E}_{q_\theta(z|x)}[log_{p_\theta}(x|z)]
\end{equation}

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[height=7cm]{media/vae_manifold-crop.pdf}
        \caption{Learned manifold using 2-dimensional latent space}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[height=7cm]{media/vae_samples-crop.pdf}
        \caption{generated images by sampling from latent space and applying $p(x|z)$}
    \end{subfigure}
    \caption{Variational autoencoder learning performance}
\end{figure*}

\subsection{Performance}
\label{sub:vae_performance}

>>>>

\section{Variational Autoencoders}
\label{sec:vae}
Variational Autoencoders (VAE) have been developed concurrently in 2014 by Kingma and Welling \cite{vae:2014} and Rezende et al\cite{dlgm:2014}.
VAEs couple a generator network with an inference network in which efficient inference and learning can be performed, thus allowing the model to be trained purely using gradient-based methods.

%which uses variational inference to perform efficient inference and learning in deep latent models.
%Deep latent models are based on the assumption that input data can be explained using non-linear transformations coming from simple distributions. \cite{rezende:2014} (check!?).

@@

\vspace{10cm}
% move to architecture:
%In the original VAE paper, the unit gaussian distribution with diagonal variance was proposed for $p(z)$ and although there have been multiple proposals (citations, multi-modal etc) for different distributions we will stick with $\mathcal{N}(0,I)$ for the sake of simplicity.
% ---

@@

%\begin{figure}[htb]
%\centering
%\includestandalone[width=\linewidth,mode=buildnew]{media/vae_multiple_layers}
  %\caption{VAE with multiple stochastic layers }\label{fig:vae_multiple_layers}
  %\medskip
  %\small
  %The left upward arrows indicate the recognition networks $q(h_1|x)$ and $q(h_2|h_1)$.
  %Note that the recognition networks can have multiple deterministic layers (including non-linearities).\\

  %$p(h_2)$ denotes the probability distribution over the highest(?) latent space.\\

  %On the right, the two conditional distributions $p(h_1|h_2)$ and $p(x|h_2)$ are representing two networks used for the generative process.
%\end{figure}

\newpage

@@

We use VAEs when we have a complicated distribution $p_\theta(x,z)$ with unknown latent variables $z$.
The prior distribution $p(z)$ over the latent structure is a centered isotropic(?) multivariate Gaussian denoted by $\mathcal{N}(z;0, I)$.
The constructed architecture uses an probabilistic encoder $q_\theta(z|x)$ and a probabilistic decoder $p_\theta(x|z)$ in a form of neural networks, in the original paper MLP are used\cite{vae:2014} but there are various extensions (see \ref{sub:vae_extensions}, TODO).
Because the posterior is intractable ($p_\theta(x)$), we instead approximately maximize the lower variational bound $L(\theta,\phi;x)$.\\
\begin{equation}
  \mathcal{L}(\theta,\phi;x) = -D_{KL}(q_\theta(z|x)||p(z)) + \mathbb{E}_{q_\theta(z|x)}[log_{p_\theta}(x|z)]
\end{equation}

\newpage

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[height=7cm]{media/vae_manifold.pdf}
        \caption{Learned manifold using 2-dimensional latent space}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[height=7cm]{media/vae_samples.pdf}
        \caption{generated images by sampling from latent space and applying $p(x|z)$}
    \end{subfigure}
    \caption{Variational autoencoder learning performance}
\end{figure*}

%\subsection{Performance}
%\label{sub:vae_performance}

\newpage

### 2016-12-19 paper/chapters/vae/iwae.tex
updated

\begin{figure}[htb]
\centering
\includestandalone[width=\linewidth,mode=buildnew]{media/vae_multiple_layers}
  \caption{VAE with multiple stochastic layers }\label{fig:vae_multiple_layers}
  \medskip
  \small
  The left upward arrows indicate the recognition networks $q(h_1|x)$ and $q(h_2|h_1)$.
  Note that the recognition networks can have multiple deterministic layers (including non-linearities).\\

  $p(h_2)$ denotes the probability distribution over the highest(?) latent space.\\

  On the right, the two conditional distributions $p(h_1|h_2)$ and $p(x|h_2)$ are representing two networks used for the generative process.
\end{figure}
% write about k passes (just averages)

@@

>>>>

% write about k passes (just averages)

@@

\vspace{5cm}
